maze-dataset

### 2025-03-30 docs/paper/paper.tex
wip

\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\usepackage{graphicx}
\usepackage{tikz}
\usepackage[luatex, pdfversion=1.7]{hyperref}
\usetikzlibrary{calc}
\tikzset{ % Define a TikZ style for an external hyperlink node.
  hyperlink node url/.style={
    alias=sourcenode,
    append after command={
      let \p1 = (sourcenode.north west),
          \p2 = (sourcenode.south east),
          \n1 = {\x2-\x1},
          \n2 = {\y1-\y2} in
      node[inner sep=0pt, outer sep=0pt, anchor=north west, at=(\p1)]
          {\href{#1}{\XeTeXLinkBox{\phantom{\rule{\n1}{\n2}}}}}
    }
  }
}
\providecommand{\XeTeXLinkBox}[1]{#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth,height=\textheight]{../benchmarks/figures/gridsize-vs-gentime.pdf}
\caption{Plots of maze generation time. Generation time scales
exponentially with maze size for all algorithms (left). Generation time
does not depend on the number of mazes being generated, and there is
minimal overhead to initializing the generation process for a small
dataset (right). Wilson's algorithm is notably less efficient than
others and has high variance. Note that for both plots, values are
averaged across all parameter sets for that algorithm, and
parallelization is disabled.}
\end{figure}

\begin{figure}
\centering
\includegraphics{../benchmarks/figures/n_mazes-vs-gentime.pdf}
\caption{Maze size vs generation time}
\end{figure}

>>>>

\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{calc}
\tikzset{ % Define a TikZ style for an external hyperlink node.
  hyperlink node url/.style={
    alias=sourcenode,
    append after command={
      let \p1 = (sourcenode.north west),
          \p2 = (sourcenode.south east),
          \n1 = {\x2-\x1},
          \n2 = {\y1-\y2} in
      node[inner sep=0pt, outer sep=0pt, anchor=north west, at=(\p1)]
          {\href{#1}{\XeTeXLinkBox{\phantom{\rule{\n1}{\n2}}}}}
    }
  }
}
\providecommand{\XeTeXLinkBox}[1]{#1}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

@@

\begin{figure}
\centering
\includegraphics[width=0.95\textwidth,height=\textheight]{docs/benchmarks/figures/gridsize-vs-gentime.pdf}
\caption{Plots of maze generation time. Generation time scales
exponentially with maze size for all algorithms (left). Generation time
does not depend on the number of mazes being generated, and there is
minimal overhead to initializing the generation process for a small
dataset (right). Wilson's algorithm is notably less efficient than
others and has high variance. Note that for both plots, values are
averaged across all parameter sets for that algorithm, and
parallelization is disabled.}
\end{figure}

\begin{figure}
\centering
\includegraphics{docs/benchmarks/figures/n_mazes-vs-gentime.pdf}
\caption{Maze size vs generation time}
\end{figure}
